---
title: "buffeRs basic usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{buffeRs basic usage}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

### buffeRs basic use

buffeRs will create non-standard buffer geometries around an input point (created by the `sf` package), and has the following functions:

1.  `buffer_wedge()` creates a wedge-shaped geometry
1.  `buffer_semicircle()` creates a semicircular geometry
1.  `buffer_windrose()` creates a windrose shaped geometry
1.  `buffer_rectangle()` creates a rectangular shaped geometry
1.  `buffer_square()` creates a square shaped geometry


One example would be to build a wedge-shaped buffer with `buffer_wedge()`.

```{r, warning = FALSE, echo = TRUE, results = "hide"}
library(buffeRs)
example(buffer_wedge)
```

We can also create a different wedge, like this:


```{r, warning = FALSE, echo = TRUE, results = "hide"}
buffer_wedge(point = example_point, radius = 200, degree = 227, degree_width = 25) -> example_wedge2
plot(example_wedge2)
```


Other geometries are similarly straightfoward, and all functions have parameters to change the radius and the angle of the object.

`buffer_windrose()` is more complex, and requires the input of a wind frequency table, in the format provided by `openair::windRose()$data`

```{r, warning = FALSE, echo = TRUE, results = "hide"}
example(buffer_windrose)
```